A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-06-01 Paper/paper.tex
Text under headings, more little tweaks

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}

@@

\subsection{Nightwatch}
The choice for Nightwatch was an easy one. First and foremost there were not very many options and the options we did have sorted themselves out.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Product 
%%% User Manual
%%%   Tools (programs, IDEs, scripts)
%%%   Setup instructions
%%%   Usage
%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Product}

\section{Our Setup}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  \item Processor: 2.53 GHz Intel Core 2 Duo
  \item Memory: 4 GB 1067 MHz DDR3
  \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow can be used on a very run-of-the-mill laptop with generally sub-standard specs. Or at the very least, an average, everyday laptop.

To carry out the development we used a combination of the OS X terminal, Sublime Text, and Netbeans. The terminal was used mainly for starting Node services, testing tools, Grunt scripts, and updating modules. Sublime Text was used to write the unit tests and the UI tests. Netbeans was used to look at the overall project as it had already been set up in Netbeans and was easy to browse therein.

@@

We decided to install everything globally because it made writing our scripts easier, but it's not a requirement. Everything can be done with locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH_TO_REPO/node_modules/MODULE_NAME/bin/MODULE_NAME} or something similar.

\subsection{Setting up Mocha}
To install Mocha, type into the terminal: \lstinline{npm install -g mocha}. The \lstinline{-g} means to install the module globally.

@@

To get Chai running with Mocha, just \lstinline{require(...)} the appropriate chai assertion method in the test and start writing. For example, to get the Assert library: \lstinline{var assert = require('chai').assert;}

After the tests have been written, the developer can run them using the \lstinline{mocha} command. There are a number of command-line arguments available to the mocha command which are well documented and which we won't talk about here. We will talk about the one that we used consistently, that being \lstinline{-R}. The \lstinline{-R} arguments allows the developer to specify how the test results will be formatted. Mocha offers seventeen different reporters with more reporters available online and the ability to create custom reporters.

\subsection{Setting up MagnumCI}
Setting up MagnumCI is painless. Visit ``magnum-ci.com'', create an account, sign in, click on ``Add a New Project''.

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_new_project.png}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}

\end{Figure}
There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}

\end{Figure}
After that setup, our project is ready to go. Anytime we commit from then on, MagnumCI will run and notify us of successful and unsuccessful builds.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are available on their developer guide. \cite{NightwatchJS}

\subsection{Setting up Istanbul}
As mentioned in the Istanbul section, getting it running is simple. Install Istanbul with npm: \lstinline{npm install -g istanbul} and then run the istanbul command along with any others needed. In our case, we ran \lstinline{istanbul cover mocha -- . -R spec} to run Istanbul on our Mocha unit tests.

\subsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is likely the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a JavaScript file called ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''.

@@

@@

\section{Workflow}
In addition to just the a list of tools and installation instructions, we'd like to propose a way to use those tools that is efficient and nearly autonomous. Our goal is to bring testing tools into use with as little resistance as possible. With a bit of effort at the outset, testing can become a crucial and enjoyable part of development.

@@

  var defaultTestSrc = grunt.config('mochaTest.test.src');
  grunt.event.on('watch', function(action, filepath) {
      grunt.config('mochaTest.test.src', defaultTestSrc);
      if (filepath.match('test/functional')) {
        grunt.config('mochaTest.test.src', filepath);
      }
  });

@@

Our gruntfile is more complex than just that, but those are the parts that make the test-on-save functionality work. As we said earlier, Grunt has a lot of plugins that are available. We use one here to make our lives easier, \lstinline{grunt-mocha-test}. It is installed, once again, through npm and gives us access to the now-built-in task \lstinline{mochaTest}. The run-on-save functionality comes from the \lstinline{watch} tasks which has \lstinline{mochaTest} in its \lstinline{tasks} array.

@@

For running the browser tests, we recommend using your CI tool. With some setup on your CI of choice, you can get Nightwatch running. Most CI setups have either Firefox pre-installed or Xvfb (a windowless X11 process) and all that's required is to install Firefox if needed and start the selenium server using Xvfb is needed. For the CI setup, after installing all the prerequisites, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} or something more suited to the developer's liking. Make sure the \lstinline{DISPLAY} environment variable is exported, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then start your selenium server, \lstinline{java -jar path/to/selenium.jar} and it's all set. Finally, run Nightwatch and rejoice.

@@

%%%%%%%%%%%%%%%%%%
%%% Evaluation
%%% PX Intro
%%%	Outline test suites
%%% PX Test metrics/results
%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}

\section{PolyXpress (PX)\cite{PX}}
Our major evaluation application was an in-house application called PolyXpress (PX). As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Because the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

@@

The Author is a tool to create one's own stories. Because our tests revolved around the Author, we'll be discussing it in depth in the following section, so to avoid redundancy, we'll say nothing else here.

The PointFinder is a tool a user can use to select GPS points based on their current location. Setting points when authoring stories can be done by clicking on a map or using points saved in the PointFinder.

\subsection{PolyXpress Author}
Our tests covered the Authoring portion of PolyXpress. PolyXpress is a completely open application where users can publish and share their stories with the world of just among friends.

@@

In regards to the underlying code, the Author tool is made up of three parts, the Controller, the Model, and the Server. The Model is more-or-less just a list that stores events, chapters, and stories and has retrieval and insertion methods. The Controller orchestrates the interactions between the Server and Model and the web page. The Server stores and retrieves information from the backing database.

@@

The goal of a unit test, is to test the function, module, or ``unit'' in isolation. While this sounds great in theory, things tend to get messier when it comes to the actual code. The method we used to alleviate this issue was to create mock functions and objects. Mocks are stand-in pieces of code that get called instead of the real implementation. Mocks are highly controlled and often just simply return the same value regardless of parameters or prior calls. Mock functions are just as their name implies, a function with a known return value regardless of parameters that is named the same things as what the unit is calling. Mock objects are objects with attributes and functions that the unit interacts with instead of the real object it will interact with in production.

@@

\section{Testing Frameworks}

@@

\todo{Finish reading this paper... My bad Dr. Haungs.}

@@

%%%%%%%%%%%%%%%%%
%%% Appendices
%%% Actual Test Code
%%% Anything that needs an appendix
%%%%%%%%%%%%%%%%%
\chapter{Appendices}

>>>>

\normalsize
%%%%%%%%%%%%%%%%%%%%%%
%%% Implementation 
%%%   Why we chose the tools we chose
%%%   Scripts written to help out 
%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
In this chapter, we will outline our final choices for frameworks and why we chose them.

@@

\subsection{Nightwatch}
The choice for Nightwatch was an easy one. First and foremost there were not many options and the options we did have sorted themselves out.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Product 
%%% User Manual
%%%   Tools (programs, IDEs, scripts)
%%%   Setup instructions
%%%   Usage
%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Product}
In this section we will mention our development setup, discuss how to set up the chosen tools, and outline our recommended workflow using the tools. It is our hope that after finishing this section, the reader will be able to install and run the chosen tools and have a good grasp of what the next steps are for their particular project.

\section{Our Setup}
The following are the specs of the laptop that we used for the entirely of this research and implementation:
\begin{itemize}
  \item Model: 15-inch Macbook Pro, Late 2008
  \item OS: OS X 10.9.2, Mavericks
  \item Processor: 2.53 GHz Intel Core 2 Duo
  \item Memory: 4 GB 1067 MHz DDR3
  \item Graphics: NVIDIA GeForce 9400M 256 MB
\end{itemize}
The point of listing the laptop specs is to show that our research and workflow was completed on an average, everyday laptop and does not require any kind of special hardware or software configurations.

To carry out the development we used a combination of the OS X terminal, Sublime Text, and Netbeans. The terminal was used mainly for starting Node services, testing tools, Grunt scripts, and for updating modules. Sublime Text was used to write the unit tests and the UI tests. Netbeans was used to quickly navigate through the code as it had already been set up as a series of Netbeans projects.

@@

We decided to install the node modules globally because it made writing our scripts easier, but it's not a requirement. Tests can be executed using locally installed node modules. Instead of using the command by itself, the developer would just need to supply the full path to the executable, which is generally \lstinline{PATH_TO_REPO/node_modules/MODULE_NAME/bin/MODULE_NAME} \space .

\subsection{Setting up Mocha}
To install Mocha, type into the terminal: \lstinline{npm install -g mocha}. The \lstinline{-g} means to install the module globally. The developer need simply skip the \lstinline{-g} in all of the following install commands if they want the modules installed locally.

@@

To get Chai running with Mocha, just \lstinline{require(...)} the appropriate chai assertion method in a test file and start writing. For example, to get the Assert library: \lstinline{var assert = require('chai').assert;}

After the tests have been written, the developer can run them using the \lstinline{mocha} command. There are a number of command-line arguments available to the mocha command which are well documented and which we won't talk about here. We will talk about the one that we used consistently, that being \lstinline{-R}. The \lstinline{-R} argument allows the developer to specify how the test results will be printed and formatted. Mocha offers seventeen different reporters with more reporters available online and the ability to create custom reporters. We used the \lstinline{spec} reporter because it gave us the information we wanted. All together, our mocha test command was \lstinline{mocha -R spec .}, the final \lstinline{.} being the directory where the tests are located.

\subsection{Setting up MagnumCI}
Setting up MagnumCI is all done online. Visit ``magnum-ci.com'', create an account, sign in, click on ``Add a New Project''.

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_new_project.png}
\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build.png}
\end{Figure}

There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{npm install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.95\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}

After that setup, the project is ready to go. Anytime a commit is pushed from then on, MagnumCI will run and notify the developer of successful and unsuccessful builds.

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are discussed in their developer guide. \cite{NightwatchJS}

\subsection{Setting up Istanbul}
As mentioned in the Istanbul section, getting it running is simple. Install Istanbul with npm: \lstinline{npm install -g istanbul} and then run the istanbul command along with any others needed. In our case, we ran \lstinline{istanbul cover mocha -- . -R spec} to run Istanbul on our Mocha unit tests. For a more detailed view of possible commands and arguments, the developer can check out the Istanbul page. \cite{Istanbul}

\subsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a JavaScript file named ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''. \cite{GruntJS}

@@

In this simple Gruntfile, all that is happening is some configuration and the creation of an ``uglify'' task that will obscure the code when run.

@@

\section{Workflow}
In addition to just a list of tools and installation instructions, we'd like to propose a way to use those tools that is efficient and nearly autonomous. Our goal is to bring testing tools into use with as little resistance as possible. With a bit of effort at the outset, testing can become a crucial and enjoyable part of development.

@@

  // Specify the test directory for Watch to keep track of
  var defaultTestSrc = grunt.config('mochaTest.test.src');
  grunt.event.on('watch', function(action, filepath) {
      grunt.config('mochaTest.test.src', defaultTestSrc);
      if (filepath.match('test/functional')) {
        grunt.config('mochaTest.test.src', filepath);
      }
  });

@@

Our gruntfile is more complex than just that, but those are the parts that make the test-on-save functionality work. As we said earlier, Grunt has a lot of plugins that are available. We use one here to make our lives easier, \lstinline{grunt-mocha-test}. It is installed, once again, through npm and gives us access to the now-built-in task \lstinline{mochaTest}. The run-on-save functionality comes from the \lstinline{watch} task which has \lstinline{mochaTest} in its \lstinline{tasks} array.

@@

For running the browser tests, we recommend using the CI tool. With some setup on the CI of choice, the developer can get Nightwatch running. Most CI setups have either Firefox pre-installed or Xvfb (a windowless X11 process). All that's required is to install Firefox if needed and create an X11 window using Xvfb if needed. In the CI setup, after installing all the prerequisites, the developer should start their application. Next, export the \lstinline{DISPLAY} environment variable, \lstinline{export DISPLAY=:99} (the numbers need to match between the xvfb call and the export). Then, run \lstinline{Xvfb :99 -ac -screen 0 1280x1024x24 &} to start the ``window'' that will be used. Finally, run Nightwatch, \lstinline{nightwatch -c path_to_nightwatch_config} and enjoy UI testing that doesn't take over the workstation.

@@

%%%%%%%%%%%%%%%%%%
%%% Evaluation
%%% PX Intro
%%%	Outline test suites
%%% PX Test metrics/results
%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}
After gathering the tools into a loose toolkit, we wanted to use that toolkit on an existing project of respectable size. We chose an application developed at Cal Poly called PolyXpress.

\section{PolyXpress (PX)\cite{PX}}
Our major evaluation application was an in-house application called PolyXpress (PX). As the About page says, ``PolyXpress allows you to create location-based stories, build eTours, or create restaurant guides. It is the tool that will bring people to locations in order to entertain, educate, or provide amazing deals.''\cite{PX} Users can play or create ``Stories'', each of which consists of ``Chapters''. Each chapter consists of various ``Events''. Each ``Event'' generally give the user some sort of information, in the form of text, video, audio, or a picture. After the player has chosen a story, they must physically reach certain checkpoints to unlock chapters and events. Since the application requires physical movement, it works solely on devices with GPS, generally phones and tablets. Rather than put a series of pictures showing PolyXpress here, we will put them in the appendix at the end of the paper. To get a better sense of what PolyXpress does and looks like, we recommend looking at the appendix now.

@@

The Author is a tool to create one's own stories. Our tests revolved around the Author, so we'll be discussing it in depth in the following section.

The PointFinder is a tool for users to select GPS points based on their current location. Setting points when authoring stories can be done by clicking on a map or using points saved in the PointFinder.

\subsection{PolyXpress Author}
Our tests covered the Authoring portion of PolyXpress. PolyXpress is a completely open application where users can publish and share their stories with the world.

@@

In regards to the underlying code, the Author tool is made up of three parts, the Controller, the Model, and the Server. The Model is more-or-less just a list that stores events, chapters, and stories and has retrieval and insertion methods. The Controller orchestrates the interactions between the Server, Model and the web page. The Server stores and retrieves information from the backing database.

@@

The goal of a unit test, is to test the function, module, or ``unit'' in isolation. While this sounds simple in theory, the situation is often more complicated when it comes to actual code. The method we used to alleviate this issue was to create mock functions and objects. Mocks are stand-in pieces of code that get called instead of the real implementation. Mocks are highly controlled and often just simply return the same value regardless of parameters or prior calls. Mock functions are just as their name implies, a function with a known return value regardless of parameters that is named the same things as what the unit is calling. Mock objects are objects with attributes and functions that the unit interacts with instead of the real object it will interact with in production.

@@

\section{Testing Frameworks}
The following are papers that were written about creating proprietary testing frameworks.

@@

@@

%%%%%%%%%%%%%%%%%
%%% Appendices
%%% Actual Test Code
%%% Anything that needs an appendix
%%%%%%%%%%%%%%%%%
\chapter{Appendices}
The following appendices include the test code for the ToDo application, screenshots of the various PolyXpress modules, and the PolyXpress test code.
